---
title: "Inventory Optimization"
author: "Huibo Jia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cosmoß
    toc: yes
    toc_depth: 3
    toc_float: yes

---



Clear environment of variables and packages  
=========================================

```{r}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```

Load pacakages and data 
=========================================

```{r}
# Load packages
library(tidyverse)
library(ggplot2)
library(kableExtra)
```


```{r}
demand <- read.csv("Data/demand.csv")
#annual_demand <- read.csv("Data/annual_demand.csv")
fcst_error <- read.csv("Data/fcst_error.csv")
future_fcst <- read.csv("Data/future_fcst.csv")
lead_time <- read.csv("Data/lead_time.csv")
#item_location_count <- read.csv("Data/item_location_count.csv")
ots <- read.csv("Data/ots.csv")
part_info <- read.csv("Data/part_information.csv")
protected_inventory <- read.csv("Data/protected_inventory.csv")

```

```{r}
summary(demand)
```

+ Most reginal orders are filled
+ 2017 to 2019-7


```{r}
summary(fcst_error)
```

+ 2017-9 to 2019-6
+ total forecast quantity negative value? (fcst_total)

```{r}
summary(lead_time)
```

+ avg_lead_time negative value?
+ shipdate supplier to paccar right?

```{r}
summary(ots)
```
+ total_all is not the sum of early, on_time, pd_shipped, past_due, >=<
+ should only focus channel PDC （28306）

```{r}
summary(part_info)
```
+ may consider group by marketing_category
+ there's products does not belong to marketing_category


```{r}
summary(protected_inventory)
```
+ protected means that the part number can not be scrapped. It has to stay in the warehouse.
+ protected_ind	an indicator to identify if the part number is protected in the system	"1 = True
0 = False"; all item in the data protected_ind= 1

+ Dimensions: time, market_category or velocity
+ metrics:r_fill,n_fill,ots, total cost of inventry, turnover of inventory: demand/no.inventory
+ forecast= forecast_daily *lead_time
+ Also show the highlighted part in the current state
+ service level: ots, rhit


State of LAN
=========================================

```{r}
# rfill rate, nfill rate, rhit cost
fill_rate <- demand %>%
  mutate(year = format(as.Date(order_month), "%Y")) %>%
  group_by(year,division) %>%
  summarise(rfill_rate = 1 - sum(rhit) / sum(rline),
        nfill_rate = 1 - sum(nhit) / sum(nline),
        rhit_cost = sum(rhit) * 15)
  
```

```{r}
# OTS is often seen as a percentage:
# (early + on_time + pd_shipped) / (past_due + total_all) 
ots[is.na(ots)] <- 0
ots$pd_shipped[ots$pd_shipped==""] <- 0
ots_pdc <- ots %>% 
  filter(channel == 'PDC') %>%
  mutate(year = format(as.Date(ots_month,"%m/%d/%Y"), "%Y")) %>%
  group_by(year) %>%
  summarise(ots = sum(early + on_time + pd_shipped) / sum(past_due + total_all))
  
```

```{r}
demand_all <- demand %>% left_join(part_info, by = c('dim')) 
```


```{r}
# 
# demand_dim <- demand %>%
#   select(dim) %>%
#   distinct()
# part_info_demand <- demand_dim %>% left_join(part_info, by = c('dim')) 
part_info_1 <- demand_all %>%
  filter(days_on_hand >0 ) %>%
  group_by(dim, velocity, marketing_category) %>%
  summarise (rate = mean(days_on_hand)/mean(lead_time))

part_info_2 <- demand_all %>%
  filter(days_on_hand >0 ) %>%
  group_by(marketing_category) %>%
  summarise (rate = mean(days_on_hand)/mean(lead_time))
```

```{r}
fcst_error_records <- fcst_error %>%
  select(dim) %>%
  distinct()
```

```{r}
# A, B, C category

```



